Verification of Stencil Computations through Spatial Specifications

### 2016-07-05 paper.tex

Given the set $\textsf{regions}(M)$ of spans covering the indexing
space, the next step converts these into abstract syntax trees
for the specification language. This conversion is defined in terms
of an algebra on \textit{specTop} syntax which mirrors the shape
of the syntax with additive and multiplicative binary operators
$\oplus$ and $\odot$: 
%%
\begin{align*}
\oplus & : \textit{specTop} \rightarrow \textit{specTop} \rightarrow
  \textit{specTop} \\
\odot & : \textit{specTop} \rightarrow \textit{specTop} \rightarrow
        \textit{specTop} \\
\mathsf{toSpec} & : (\mathbb{Z} \cup \{\infty\}) \rightarrow (\mathbb{Z} \cup
  \{\infty\})  \rightarrow \textit{specTop}
\end{align*}
%%
The operation $\mathsf{toSpec}$ takes a pair of lower and upper bounds
values and produces a specification which contains a one-dimensional
region. The

$\oplus$ and $\odot$ respectively (defined in Definition~\ref{}
and Definition~\ref{} below).

The proceeds by converting each span
into a specification by converting ea
 is mapped to a specification,
and then summing specifications. This relies on product and sum
operations lifted to specification syntax (which is more than just
building regions out of \term{*} and \term{+}).

\begin{equation*}
\sum\limits_{\vect{x} \in \textsf{regions}(M)}
\prod\limits_{i \in \{1, \ldots, n\}} \, \mathsf{toSpec}(\vect{x}^L_i, \vect{x}^U_i)
\end{equation*}

@@

\begin{equation*}
{\Large{\bullet}}_{i \in \{1, \ldots, n\}} \, \mathsf{toSpec}(\vect{x}^L_i, \vect{x}^U_i)
\end{equation*}

>>>>

Given the set $\textsf{regions}(M)$ of spans covering the indexing
space, the next step converts these into abstract syntax trees
for the specification language. This conversion is defined in terms
of an algebra on \textit{specTop} syntax which mirrors the shape
of the syntax with additive and multiplicative binary operators
$\oplus$ and $\odot$ and a constructor for \textit{specTop}:
%%
\begin{align*}
\oplus & : \textit{specTop} \rightarrow \textit{specTop} \rightarrow
  \textit{specTop} \\
\odot & : \textit{specTop} \rightarrow \textit{specTop} \rightarrow
        \textit{specTop} \\
\mathsf{toSpec} & : (\mathbb{Z} \cup \{\infty\}) \rightarrow (\mathbb{Z} \cup
  \{\infty\})  \rightarrow \textit{specTop}
\end{align*}
%%
The operation $\mathsf{toSpec}$ takes a pair of lower and upper bounds
values and constructs a specification which contains a one-dimensional
region. This step of the inference then proceeds by converting each
span into a $n$-dimensional specification by converting each
pair of bounds in a span and multiplying by $\otimes$
then summing the specifications resulting specification by $\oplus$.
That is: 
\begin{equation*}
\textit{spec}(M) = 
\sum\limits_{\vect{x} \in \textsf{regions}(M)}
\prod\limits_{i \in \{1, \ldots, n\}} \, \mathsf{toSpec}(\vect{x}^L_i, \vect{x}^U_i)
\end{equation*}

@@
